\section{Conclusions}
\label{sec:conclusions}

If I want to maximize my winning changes against stronger opponents I should play with white pieces against them and select standard chess with long time control as our variant. I might also consider timing our game at around 2 PM to benefit from my daily cup of coffee but otherwise timing wasn't shown in my analysis to make a difference.

In addition some less certain observations were made from data. Connection between game ending in a draw and having black pieces can be questioned based on small number of data points since naturally there are a lot less games that end in a draw than games that end in a victory or loss. Also some results suggested connection between higher likelihood of losing and playing crazyhouse variant but other results were against such conclusion. MCA is nonrobust method but I don't see issues with using it in my data as it had a good amount of data points for performing analysis and our variables had at maximum two or three modalities. Therefore in other respects I am quite confident in my results.

Possible further research could be related on how decisions in data preprocessing affect results. For example time of day could be aggregated to more fine grained categories than just three categories. Similarly changing threshold rating difference on what we consider stronger opponent could lead to new insights. Also similar analysis for other chess variants than discussed here would be interesting but it would also require more data.